---
title: "Week 10 Task Set"
author: "Deano Izaguirre"
format: html
execute:
  echo: true
  warning: true
  message: true
---

#### Q1: Load and Inspect Data ------------------------------------

```{r}
## Load the saved dataset
experiment_data <- readRDS("../data/raw/experiment_data.rds")

## Take a quick look at the first few rows
head(experiment_data)

## Check the structure of the dataset
str(experiment_data)
```
#### Q2: Functions ------------------------------------------------

```{r}
## Generate one or more random numbers between min and max (defaults: one number between 1–10)
getRandomNumber <- function(min = 1, max = 10, number = 1) {
  sample(min:max, number)
}
```

```{r}
## Classify reaction times into "Fast", "Slow", or "Unknown" (default threshold = 500ms)
experiment_data$rt_category <- NA ## create new column for rt category
classify_rt <- function (rt, threshold = 500) {
  if (!is.numeric(rt)) { ## input validation for making sure rt is numeric
    stop("Error: 'rt' must be numeric.")
  } 
  if (!is.numeric(threshold) || length(threshold) != 1) { ## input validation for making sure threshold is single numeric value
    stop("Error: 'threshold' must be a single numeric value.")
  }
  ifelse( ## conditional code for categorizing reaction times, vectorized for efficiency
  is.na(rt), "Unknown",
  ifelse (rt < threshold, "Fast", "Slow")
  )
}
experiment_data$rt_category <- classify_rt(experiment_data$rt, 500)
```

#### Q3: Loops vs. Vectorization -----------------------------
```{r}
experiment_data$age <- NA ## create new column called age and populate w/ NA
```

```{r}
for (i in 1:nrow(experiment_data)) {
experiment_data[i, "age"] <- getRandomNumber(18, 65, 1) ## sample a random number for as many rows as in the "age" column
}
head(experiment_data)
```

```{r}
experiment_data$age <- sample(18:65, replace = TRUE, nrow(experiment_data)) ## sample as many rows as are in the df
head(experiment_data)
```

## Q4: Control Structures on Data Frames ---------------------------
```{r}
experiment_data$rt_category_loop <- NA ## create an empty column and populate with NA
for (i in 1:nrow(experiment_data)) { ## fill empty column row by row using classify_rt
 experiment_data[i, "rt_category_loop"] <- classify_rt(experiment_data[i, "rt"], 500) ## classify using individual value of every row of rt
}
```

```{r}
experiment_data$rt_category_vec <- NA ## create empty column and populate w/ NA
experiment_data$rt_category_vec <- classify_rt(experiment_data$rt, threshold = 500) ## fill using classify_rt
```

```{r}
table(loop = experiment_data$rt_category_loop,
      vec  = experiment_data$rt_category_vec,
      useNA = "ifany")
```
#### Q5: Debugging Functions -----------------------------
```{r}
## Create Buggy Function
threshold <- 500

flag_fast <- function(rt_vector) {
  rt_vector < threshold
}

flag_fast(experiment_data$rt)
```
# ```{r}
# rm(threshold)
# 
# flag_fast(experiment_data$rt)
# ```
```{r}
flag_fast <- function(rt_vector, threshold = 500) {
  rt_vector < threshold
}
# rm(threshold)

flag_fast(experiment_data$rt)
```
#### Q6: Debugging Tools in Action -----------------------------
```{r}
subject_means <- tapply(experiment_data$rt,
                        experiment_data$condition,
                        mean)
print(paste("Mean for control:", subject_means["control"]))
print(paste("Mean for incongruent:", subject_means["incongruent"]))
```
```{r}
# How many NAs overall?
sum(is.na(experiment_data$rt))

# How many NAs by condition?
tapply(is.na(experiment_data$rt), experiment_data$condition, sum)

# Optional: quick sanity checks
summary(experiment_data$rt)
with(experiment_data, table(condition, is.na(rt)))
```
```{r}
subject_means <- tapply(experiment_data$rt,
                        experiment_data$condition,
                        function(x) mean(x, na.rm = TRUE)) ## define anonymous function to be used in tapply so we can apply mean AND na.rm at the same time
print(paste("Mean for control:", subject_means["control"]))
print(paste("Mean for incongruent:", subject_means["incongruent"]))
```

#### Q7: Using AI for Debugging or Refactoring -----------------------
### ```{r}
### subject_means <- tapply(experiment_data$rt, ## reusing this buggy code
                        experiment_data$condition,
                        mean)
### print(paste("Mean for control:", subject_means["control"]))
### print(paste("Mean for incongruent:", subject_means["incongruent"]))
### ```

## Evaluating ChatGPT's response: The AI did a good job breaking down the problem into digestible and easy-to-follow instructions, offering a general explanation for what went wrong first before going into detail. I did verify because we were taught to use an anonymous function to include na.rm in tapply, so I was a bit skeptical that it would work, but tapply still worked just fine even without the anonymous function. I made sure the outcome was correct by comparing it with this anynomous function path that I used earlier to make sure I got the same result.

```{r}
## fixed code from ChatGPT
subject_means <- tapply(experiment_data$rt,
                        experiment_data$condition,
                        mean,
                        na.rm = TRUE)
print(paste("Mean for control:", subject_means["control"]))
print(paste("Mean for incongruent:", subject_means["incongruent"]))
```

#### Q8: Saving and Reloading Objects -----------------------------
```{r}
write.csv(experiment_data, "../data/cleaned/experiment_data.csv", row.names = FALSE) ## save as .csv

saveRDS(experiment_data, "../data/cleaned/experiment_data.rds") ## save as .rds
```

```{r}
save(experiment_data, subject_means, file = "../data/raw/objects.RData") ## save as 
```


```{r}
rm(list = ls())
load("../data/cleaned/objects.RData")
```